FEM Transition Models

### 2023-03-16 FEM_R/Loneliness_Social_Isolation/transition_models_testing.Rmd
Expanded the mortality model with chronic diseases and risk behaviours

>>>>

I like the previous model, lets also do a few test versions.

```{r}
form.mort.test <- 'died ~ male + white + hsless + college + 
                  l2age65l + l2age6574 + l2age75p + 
                  l2lnly1 + l2lnly2 +
                  l2sociso1 + l2sociso2 + l2sociso3 + l2sociso4 + l2sociso5 +
                  l2cancre + l2diabe + l2hearte + l2alzhe + l2demene + l2lunge +
                  l2stroke + l2smokev + l2smoken + l2smokef'

probit.mort.test <- glm(formula = form.mort.test, family = binomial(link = 'probit'),
                    data = trans)

summary(probit.mort.test)
```
